On the Synchronization of Computational RFIDs

### 2018-05-13 TMC-2017-11-0695-main.tex
Section 1.1 of the paper revised

\add{Since we are not aware of any network infrastructure to demonstrate neither multi-hop communication nor multi-hop synchronization, our focus in this article is the networks where several readers cover a tag population simultaneously. A representative greenhouse monitoring application where several tags are powered by two readers is depicted in Figure~\ref{fig:motivation}. In this application, the tags sense the environment and timestamp their temperature readings. When the readers request their temperature readings, the tags transmit their timestamps together with the collected temperature data. In order to make inferences on the collected temperature readings, timestamps should be consistent so that the readers can provide a temporal ordering of the readings. Therefore, tags require a common time notion to timestamp their readers---creating an demand for explicit time synchronization. In order to achieve synchronization, first readers should acquire the global time, .e.g. by accessing time servers using the Internet; then individual tags should be synchronized to the individual readers.}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\columnwidth]{figures/scenario.pdf}
	\caption{\label{fig:motivation}\color{blue}A representative greenhouse monitoring application using CRFIDs. Two readers are deployed to provide power to the individual tags and to collect their periodic sensor readings.}
\end{figure}

>>>>

\add{Since we are not aware of any network infrastructure demonstrating neither multi-hop communication nor multi-hop synchronization, our focus in this article are the CRFID networks where several readers cover a tag population simultaneously in a single hop. A representative application is the greenhouse monitoring where several tags are powered by multiple readers, see Figure~\ref{fig:motivation}. In this application, the tags sense the environment and timestamp their temperature readings. When the readers request their temperature readings, the tags transmit their timestamps together with the collected temperature data. In order to make inferences on the collected temperature readings, timestamps should be consistent so that the readers can provide a temporal ordering of the readings. Therefore, tags require a common time notion to timestamp their readers---creating a demand for explicit time synchronization. In order to achieve synchronization, readers should first acquire the global time, e.g. by accessing time servers using the Internet; then individual tags should be synchronized to the individual readers.}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/scenario.pdf}
	\caption{\label{fig:motivation}\color{blue}A representative greenhouse monitoring application using CRFIDs. Two readers are deployed to provide power to the individual tags and to collect their periodic sensor readings.}
\end{figure}
